Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-22 ms.tex
re-write of unit conversion subsection

\begin{figure}
\begin{center}
\epsfig{file=scatter_857_217.eps, width=3.3in}
\caption{\label{fig:scatter} Scatter plot of \PLANCK~217 GHz versus \PLANCK~857
GHz. Left: before correcting for offset and residual Solar dipole. Right: after
correcting or the best-fit offset and dipole amplitude, as described in 
$\S$\ref{sec:zp}. The dashed red line shows the best-fit linear relationship
between 857 GHz and 217 GHz.}
\end{center}
\end{figure}

The offset and residual dipole parameters for \PLANCK~217 GHz were not 
available from \cite{planckdust} Table 1. In order to set the zero-point of 
Galactic emission in the 217 GHz map, we simultaneously fit the constant 
offset and residual dipole amplitude. Restricting to regions of low column 
density (H\,\textsc{i} $<$ 200 K km/s), we modeled the 217 GHz map as:

%in previous sentence, mention the specific cut on HI velocities considered

@@

Some of the maps in native format are provided in thermodynamic $\delta T$, 
while others are provided in units of MJy/sr. Before performing any fits, 
we convert all measurements to MJy/sr following the guidelines of 
\cite{planckresponse}.

%i think it's table 5 that I specifically want to cite within the ``spectral
%response'' paper, but i need to check that those values are consistent
% with the ones i actually used from the other document ``HFI-unit conversion 
%and colour correction instructions v1.2''

>>>>

\begin{figure}
\begin{center}
\epsfig{file=scatter_857_217.eps, width=3.4in}
\caption{\label{fig:scatter} Scatter plot of \PLANCK~217 GHz versus \PLANCK~857
GHz. Left: before correcting for offset and residual Solar dipole. Right: after
correcting or the best-fit offset and dipole amplitude, as described in 
$\S$\ref{sec:zp}. The dashed red line shows the best-fit linear relationship
between 857 GHz and 217 GHz.}
\end{center}
\end{figure}

The offset and residual dipole parameters for \PLANCK~217 GHz were not 
available from \cite{planckdust} Table 1. In order to set the zero-point of 
Galactic emission in the 217 GHz map, we simultaneously fit the constant 
offset and residual dipole amplitude. Restricting to regions of low column 
density (H\,\textsc{i} $<$ 200 K km/s for $-72$$<$$v_{LSR}$$<$$+25$ km/s), we 
modeled the 217 GHz map as:

@@

The \PLANCK~217 GHz and 353 GHz data are provided in thermodynamic $\delta T$, 
while \verb|i100| and the higher frequency \PLANCK~maps are provided in units 
of MJy/sr. Although the aforementioned preprocessing steps were conducted with 
each map in its native units, we converted the 217 GHz and 353 GHz 
measurements to MJy/sr according to \cite{planckresponse} prior to performing 
SED fits.

%i think it's table 6 that I specifically want to cite within the ``spectral
%response'' paper, but i need to check that those values are consistent
% with the ones i actually used from the other document ``HFI-unit conversion 
%and colour correction instructions v1.2''
